---
title: "Getting started with binomial"
author: "Ewen Dai"
date: "May 2, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Binomial

This is a R package that models the binomial and relates to the number of successes and a fixed number of trials and probability.

## Creating a Binomial Variable

You can create a binomial variable using the `bin_variable()` function.
```{r}
var = bin_variable(4, 0.5)
var
```

## Computations with `trials` and `prob`

Given `trials` and `prob`, the number of trials and the value of probability, the following functions can be used:
*`bin_distribution(trials, prob)`: calculates the probability distribution of binomial(trials, prob)
*`bin_cumulative(trials, prob)`: calculates the cumulative distribution of binomial(trials, prob)
*`bin_mean(trials, prob)`: calculates the mean of binomial(trials, prob)
*`bin_variance(trials, prob)`: calculates the variance of binomial(trials, prob)
*`bin_mode(trials, prob)`: calculates the mode of binomial(trials, prob)
*`bin_skewness(trials, prob)`: calculates the skewness of binomial(trials, prob)
*`bin_kurtosis(trials, prob)`: calculates the kurtosis of binomial(trials, prob)

```{r}
trials = 10
prob = 0.5
bin_distribution(trials, prob)
bin_cumulative(trials, prob)
bin_mean(trials, prob)
bin_variance(trials, prob)
bin_mode(trials, prob)
bin_skewness(trials, prob)
bin_kurtosis(trials, prob)
```

## Considering Successes

`bin_choose(n, k)` and `bin_probability(success, trials, prob)` have to do with the number of successes.

`bin_choose(n, k)` calculates the total different combinations of `k` successes in `n` trials.
```{r}
bin_choose(10, 3)
```

`bin_probability(success, trials, prob)` calculates the total probability of `success` successes in `trials` trials with `prob` probability.
```{r}
bin_probability(3, 10, 0.5)
```

